Unknown

### 2024-04-04 ms/ms.qmd
drafted some methods on estimating parameters

---
title: Unknown
format:
  pdf:
    keep-tex: true  
    toc: false
header-includes: |
  \usepackage{hyperref}
  \addtokomafont{disposition}{\rmfamily}
  \usepackage{siunitx}
  \newcommand{\aax}{$\mathrm{AA}$}
  \newcommand{\Aamphi}{$A_{\mathrm{amphi}}$}
  \newcommand{\Ahypo}{$A_{\mathrm{hypo}}$}
  \newcommand{\agcurve}{$A \textendash g_\text{sw}$}
  \newcommand{\aqcurve}{$A \textendash Q$}
  \newcommand{\ca}{$C_\mathrm{a}$}
  \newcommand{\caequals}[1]{$C_\mathrm{a} = \qty{#1}{\micro\mol\raiseto{-1}\mol}$}
  \newcommand{\cabetween}[2]{#1 < $C_\mathrm{a} < \qty{#2}{\micro\mol\raiseto{-1}\mol}$}
  \newcommand{\gsw}{$g_\text{sw}$}
  \newcommand{\ppfd}{$\mathrm{PPFD}$}
  \newcommand{\ppfdequals}[1]{$\mathrm{PPFD} = \qty{#1}{\micro\mol\raiseto{-2}\meter\raiseto{-1}\second}$}
  \newcommand{\ppfdqty}[1]{$\qty{#1}{\micro\mol\raiseto{-2}\meter\raiseto{-1}\second}$}
  \newcommand{\rh}{$\mathrm{RH}$}
  \newcommand{\rhequals}[1]{$\mathrm{RH} = #1\%$}
  \newcommand{\tleafequals}[1]{$T_\mathrm{leaf} = \qty{#1}{\degreeCelsius}$}
mainfont: Times New Roman
bibliography: solanum-aa.bib
csl: https://www.zotero.org/styles/science
---

@@

*Procedure*: We fit provisional nonrectangular hyperbola [@marshall_model_1980] to each \aqcurve{} curve using nonlinear regression with the `nlsLM()` function from the *R* package **minpack.lm** version `r packageVersion("minpack.lm")` [@Elzhov_minpack.lm_2023]. We sequentially removed data points with an absolute external studentized residual $> `r point_outlier_threshold`$ until none remained.

@@

We fit Bayesian models using the *R* package **brms** version `r fit_aa$version$brms` [@burkner_brms_2017] with MCMC sampling in *Stan* [@stan_development_team_stan_2023]. We used CmdStan version `r fit_aa$version$cmdstan` and **cmdstanr** version `r fit_aa$version$cmdstanr` [@gabry_cmdstanr_2023] to interface with *R* version `r getRversion()` [@r_core_team_r:_2023]. We sampled the posterior distribution from `r dim_fit_aa[2]` chains with `r dim_fit_aa[1]` iterations each after `r dim_fit_aa[1]` warmup iterations per chain. We estimated parameters and confidence intervals as the median and 95% quantile intervals of the posterior, respectively.

#### Parameter estimates (this is a provisional section)

@@

$$\mathrm{AA} = \int_{\text{min(log(}g_\text{sw}))}^{\text{max(log(}g_\text{sw}))} \text{log}\bigg(\frac{A_\text{amphi}(x; \theta_\text{amphi})}{A_\text{hypo}(x; \theta_\text{hypo})}\bigg) dx$$

>>>>

---
title: Unknown
format:
  pdf:
    keep-tex: true  
    toc: false
header-includes: |
  \usepackage{hyperref}
  \addtokomafont{disposition}{\rmfamily}
  \usepackage{siunitx}
  \newcommand{\aax}{$\mathrm{AA}$}
  \newcommand{\Aamphi}{$A_{\mathrm{amphi}}$}
  \newcommand{\Ahypo}{$A_{\mathrm{hypo}}$}
  \newcommand{\agcurve}{$A \textendash g_\text{sw}$}
  \newcommand{\aqcurve}{$A \textendash Q$}
  \newcommand{\ca}{$C_\mathrm{a}$}
  \newcommand{\caequals}[1]{$C_\mathrm{a} = \qty{#1}{\micro\mol\raiseto{-1}\mol}$}
  \newcommand{\cabetween}[2]{#1 < $C_\mathrm{a} < \qty{#2}{\micro\mol\raiseto{-1}\mol}$}
  \newcommand{\gsw}{$g_\text{sw}$}
  \newcommand{\loggsw}{$\log(g_\text{sw})$}
  \newcommand{\logA}{$\log(A)$}
  \newcommand{\ppfd}{$\mathrm{PPFD}$}
  \newcommand{\ppfdequals}[1]{$\mathrm{PPFD} = \qty{#1}{\micro\mol\raiseto{-2}\meter\raiseto{-1}\second}$}
  \newcommand{\ppfdqty}[1]{$\qty{#1}{\micro\mol\raiseto{-2}\meter\raiseto{-1}\second}$}
  \newcommand{\rh}{$\mathrm{RH}$}
  \newcommand{\rhequals}[1]{$\mathrm{RH} = #1\%$}
  \newcommand{\tleafequals}[1]{$T_\mathrm{leaf} = \qty{#1}{\degreeCelsius}$}
mainfont: Times New Roman
bibliography: solanum-aa.bib
csl: https://www.zotero.org/styles/science
---

@@

*Procedure*: We fit provisional nonrectangular hyperbola [@marshall_model_1980] to each \aqcurve{} curve using nonlinear regression with the `nlsLM()` function from the *R* package **minpack.lm** version `r packageVersion("minpack.lm")` [@elzhov_minpacklm_2023]. We sequentially removed data points with an absolute external studentized residual $> `r point_outlier_threshold`$ until none remained.

@@

We fit Bayesian models with MCMC sampling in the probabilistic programming language *Stan* [@stan_development_team_stan_2023]. We used CmdStan version `r fit_aa$version$cmdstan` and **cmdstanr** version `r fit_aa$version$cmdstanr` [@gabry_cmdstanr_2023] to interface with *R* version `r getRversion()` [@r_core_team_r:_2023]. We sampled the posterior distribution from `r dim_fit_aa[2]` chains with `r dim_fit_aa[1]` iterations each after `r dim_fit_aa[1]` warmup iterations per chain. We estimated parameters and confidence intervals as the median and 95% quantile intervals of the posterior, respectively.

#### Parameter estimation

There were four levels of parameter estimation in our analysis:

1. Estimate \agcurve{} curve parameters for each leaf
2. Estimate \aax{} for each light intensity with leaf using \agcurve{} curve parameters
3. Estimate the effects of light intensity, light treatment, and accession on \aax{} (assimilatory and plasticity hypotheses)
4. Estimate the effects of native light habitat on accession-level \aax{} (constitutive hypothesis)

Although the higher-level parameter estimates depend on the lower-level parameter estimates, we fit all models simultaneously to ensure that the uncertainty in lower-level estimates propagated to higher-level estimates.

##### \agcurve{} curve parameters

We modeled \logA as a quadratic function of \loggsw for each leaf using the following equation:

$$\log(A_{ij}) = (\beta_0 + b_{0,j}) + (\beta_1 + b_{1,j}) \log{g_{\text{sw},i}} + (\beta_2 + b_{2,j}) \log{g_{\text{sw},i}}^2 + \epsilon_{i}$$

where $\beta_0$, $\beta_1$, and $\beta_2$ are the average intercept, linear, and quadratic coefficients, respectively. We used diffuse normal priors with mean $0$ and standard deviation $10$ on these parameters. We estimated random effects of curve $j$ on the intercept ($b_{0,j}$), linear ($b_{1,j}$), and quadratic ($b_{2,j}$) coefficients. We assumed that the $j \times 3$ array of coefficients was multivariate normal a mean vector of $\vec{0}$ and covariance $\Sigma_\text{curve}$. We used a weakly informative normal prior with mean $0$ and standard deviation $1$ on the log-transformed standard deviations (i.e. the diagonal of $\Sigma_\text{curve}$). We used a weakly informative $\mathrm{LJK}(2)$ prior on the correlation matrix. The off diagonal elements of $\Sigma_\text{curve}$ can be calculated from its diagonal elements and the correlation matrix.

The residuals $\epsilon_{i}$ were modeled as a lag-1 autocorrelated time-series. We further assumed that the residual standard deviation of the $j^{\text{th}}$ curve ($\sigma_{\epsilon,j}$) was inversely proportional to the leaf surface area ($S_j$) within the chamber:

$$\log (\sigma_{\epsilon,j}) = \log (\sigma_{\qty{6}{\raiseto{2}\centi\meter},\epsilon}) + (6 - S_j) \beta_{S,\epsilon}$$
where $\sigma_{\qty{6}{\raiseto{2}\centi\meter},\epsilon}$ is the minimum residual standard deviation when the $\qty{6}{\raiseto{2}\centi\meter}$ chamber is completely filled. The residual standard deviation increases on log-linear scale by $\beta_{S,\epsilon}$. We used a weakly informative normal prior with mean $-3$ and standard deviation $5$ on $\log (\sigma_{\qty{6}{\raiseto{2}\centi\meter},\epsilon})$ and a weakly informative normal prior with mean $0$ and standard deviation $1$ on $\beta_{S,\epsilon}$.

##### \aax{} for each light intensity with leaf using \agcurve{} curve parameters

Within the $k^{\text{th}}$ leaf, we estimated \aax{} for each light intensity by integrating the difference in \logA between the amphi and pseudohypo \agcurve{} curves over the range of \gsw{} values where the curves overlap. We used the following equation to estimate \aax{} for the $k^{\text{th}}$ leaf at light intensity $l$ in accession $m$:

$$\widehat{\mathrm{AA}}_{klm} = \int_{\text{min(log(}g_\text{sw}))}^{\text{max(log(}g_\text{sw}))} \text{log}\bigg(\frac{\hat{A}_\text{amphi}(x; \theta_{klm,\text{amphi})}}{\hat{A}_\text{hypo}(x; \theta_{klm,\text{hypo})}}\bigg) dx$$
where:

$$\theta_\text{amphi} \in \{\hat{b}_{0, f(\text{amphi}, k,l,m)}, \hat{b}_{1, f(\text{amphi}, k,l,m)}, \hat{b}_{2, f(\text{amphi}, k,l,m)}\}, \text{and}$$

$$\theta_\text{hypo} \in \{\hat{b}_{0, f(\text{hypo}, k,l,m)}, \hat{b}_{1, f(\text{hypo}, k,l,m)}, \hat{b}_{2, f(\text{hypo}, k,l,m)}\}.$$ 
The function $f : \Theta_1 \rightarrow \Theta_2$ maps the set $\Theta_1$ indexed by leaf type (amphi or pseudohypo), leaf replicate, light intensity, and accession to set $\Theta_2$ indexed by individual \agcurve{} curve.

##### Effects of light intensity, light treatment, and accession on \aax

WORKING HERE

We estimated these parameters for each leaf using the posterior distribution of the parameters from the \agcurve{} curve fitting procedure.

@@

### 2024-04-04 ms/ms.tex
drafted some methods on estimating parameters

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\KOMAoption{captions}{tableheading}
\usepackage{hyperref}
\addtokomafont{disposition}{\rmfamily}
\usepackage{siunitx}
\newcommand{\aax}{$\mathrm{AA}$}
\newcommand{\Aamphi}{$A_{\mathrm{amphi}}$}
\newcommand{\Ahypo}{$A_{\mathrm{hypo}}$}
\newcommand{\agcurve}{$A \textendash g_\text{sw}$}
\newcommand{\aqcurve}{$A \textendash Q$}
\newcommand{\ca}{$C_\mathrm{a}$}
\newcommand{\caequals}[1]{$C_\mathrm{a} = \qty{#1}{\micro\mol\raiseto{-1}\mol}$}
\newcommand{\cabetween}[2]{#1 < $C_\mathrm{a} < \qty{#2}{\micro\mol\raiseto{-1}\mol}$}
\newcommand{\gsw}{$g_\text{sw}$}
\newcommand{\ppfd}{$\mathrm{PPFD}$}
\newcommand{\ppfdequals}[1]{$\mathrm{PPFD} = \qty{#1}{\micro\mol\raiseto{-2}\meter\raiseto{-1}\second}$}
\newcommand{\ppfdqty}[1]{$\qty{#1}{\micro\mol\raiseto{-2}\meter\raiseto{-1}\second}$}
\newcommand{\rh}{$\mathrm{RH}$}
\newcommand{\rhequals}[1]{$\mathrm{RH} = #1\%$}
\newcommand{\tleafequals}[1]{$T_\mathrm{leaf} = \qty{#1}{\degreeCelsius}$}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}

@@

\emph{Procedure}: We fit provisional nonrectangular hyperbola
(\textbf{marshall\_model\_1980?}) to each \aqcurve{} curve using
nonlinear regression with the \texttt{nlsLM()} function from the
\emph{R} package \textbf{minpack.lm} version 1.2.4
(\textbf{Elzhov\_minpack.lm\_2023?}). We sequentially removed data
points with an absolute external studentized residual \(> 3\) until none
remained.

@@

\begin{itemize}
\tightlist
\item
  models fit in Stan/brms
\item
  we chose the number of chains, warmup and sampling iterations, and
  maximum treedepth so that parameter estimates converged
  (\(\hat{R} < 1.01\) (\emph{8})) and the effective sample size (ESS)
  for each parameter was \(> 10^3\).
\end{itemize}

We fit Bayesian models using the \emph{R} package \textbf{brms} version
2.20.4 (\emph{9}) with MCMC sampling in \emph{Stan} (\emph{10}). We used
CmdStan version 2.33.1 and \textbf{cmdstanr} version 0.7.1 (\emph{11})
to interface with \emph{R} version 4.3.2 (\emph{12}). We sampled the
posterior distribution from 4 chains with 1000 iterations each after
1000 warmup iterations per chain. We estimated parameters and confidence
intervals as the median and 95\% quantile intervals of the posterior,
respectively.

\paragraph{Parameter estimates (this is a provisional
section)}\label{parameter-estimates-this-is-a-provisional-section}

@@

\[\mathrm{AA} = \int_{\text{min(log(}g_\text{sw}))}^{\text{max(log(}g_\text{sw}))} \text{log}\bigg(\frac{A_\text{amphi}(x; \theta_\text{amphi})}{A_\text{hypo}(x; \theta_\text{hypo})}\bigg) dx\]

@@

We tested competing predictions through a combination of model selection
and parameter estimation from the posterior of selected models. We
started with a base model that includes fixed effects of light intensity
and light treatment on \aax, a random effect of accession on \aax, and a
linear regression of PAR on accession-level \aax. We next compared the
fit of the base model to a more complex with an interaction between
light intensity and light treatment using LOOIC with the \textit{R}
package \textbf{loo} version 2.7.0 (\textbf{vehtari\_practical\_2017?}).
These comparisons allowed us to test the main predictions of each
hypothesis and for a reinforcing interactions between assimilatory and
plastic hypotheses (tab:predictions). However, these models cannot test
predictions when there is an interaction with the constitutive
hypothesis, because this hypothesis posits accession-levels variation in
responses to light intensity and/or light treatment. Therefore, we
tested for significant variation among accessions in light intensity and
light treatment by comparing LOOIC values of models with and without
random interactions between these factors and accession.

@@

\bibitem[\citeproctext]{ref-gelman_inference_1992}
\CSLLeftMargin{8. }%
\CSLRightInline{A. Gelman, D. B. Rubin, Inference from iterative
simulation using multiple sequences. \emph{Statistical Science}
\textbf{7}, 457--472 (1992).}

\bibitem[\citeproctext]{ref-burkner_brms_2017}
\CSLLeftMargin{9. }%
\CSLRightInline{P.-C. Bürkner,
\href{https://doi.org/10.18637/jss.v080.i01}{\textbf{Brms} : {An}
\emph{r} {Package} for {Bayesian} {Multilevel} {Models} {Using}
\emph{stan}}. \emph{Journal of Statistical Software} \textbf{80}
(2017).}

\bibitem[\citeproctext]{ref-stan_development_team_stan_2023}
\CSLLeftMargin{10. }%
\CSLRightInline{Stan Development Team, \emph{Stan {Modeling} {Language}
{Users} {Guide} and {Reference} {Manual}} (2023;
\url{https://mc-stan.org}).}

\bibitem[\citeproctext]{ref-gabry_cmdstanr_2023}
\CSLLeftMargin{11. }%
\CSLRightInline{J. Gabry, R. Češnovar, \emph{Cmdstanr: {R} {Interface}
to '{CmdStan}'} (2023;
\href{https://mc-stan.org/cmdstanr,\%20https://discourse.mc-stan.org}{https://mc-stan.org/cmdstanr,
https://discourse.mc-stan.org}).}

\bibitem[\citeproctext]{ref-r_core_team_r:_2023}
\CSLLeftMargin{12. }%
\CSLRightInline{R Core Team, \emph{R: {A} {Language} and {Environment}
for {Statistical} {Computing}} (R Foundation for Statistical Computing,
Vienna, Austria, 2023; \url{http://www.R-project.org/}).}

>>>>

\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}
\KOMAoption{captions}{tableheading}
\usepackage{hyperref}
\addtokomafont{disposition}{\rmfamily}
\usepackage{siunitx}
\newcommand{\aax}{$\mathrm{AA}$}
\newcommand{\Aamphi}{$A_{\mathrm{amphi}}$}
\newcommand{\Ahypo}{$A_{\mathrm{hypo}}$}
\newcommand{\agcurve}{$A \textendash g_\text{sw}$}
\newcommand{\aqcurve}{$A \textendash Q$}
\newcommand{\ca}{$C_\mathrm{a}$}
\newcommand{\caequals}[1]{$C_\mathrm{a} = \qty{#1}{\micro\mol\raiseto{-1}\mol}$}
\newcommand{\cabetween}[2]{#1 < $C_\mathrm{a} < \qty{#2}{\micro\mol\raiseto{-1}\mol}$}
\newcommand{\gsw}{$g_\text{sw}$}
\newcommand{\loggsw}{$\log(g_\text{sw})$}
\newcommand{\logA}{$\log(A)$}
\newcommand{\ppfd}{$\mathrm{PPFD}$}
\newcommand{\ppfdequals}[1]{$\mathrm{PPFD} = \qty{#1}{\micro\mol\raiseto{-2}\meter\raiseto{-1}\second}$}
\newcommand{\ppfdqty}[1]{$\qty{#1}{\micro\mol\raiseto{-2}\meter\raiseto{-1}\second}$}
\newcommand{\rh}{$\mathrm{RH}$}
\newcommand{\rhequals}[1]{$\mathrm{RH} = #1\%$}
\newcommand{\tleafequals}[1]{$T_\mathrm{leaf} = \qty{#1}{\degreeCelsius}$}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\usepackage{bookmark}

@@

\emph{Procedure}: We fit provisional nonrectangular hyperbola (\emph{8})
to each \aqcurve{} curve using nonlinear regression with the
\texttt{nlsLM()} function from the \emph{R} package \textbf{minpack.lm}
version 1.2.4 (\emph{9}). We sequentially removed data points with an
absolute external studentized residual \(> 3\) until none remained.

@@

\begin{itemize}
\tightlist
\item
  models fit in Stan/brms
\item
  we chose the number of chains, warmup and sampling iterations, and
  maximum treedepth so that parameter estimates converged
  (\(\hat{R} < 1.01\) (\emph{10})) and the effective sample size (ESS)
  for each parameter was \(> 10^3\).
\end{itemize}

We fit Bayesian models with MCMC sampling in the probabilistic
programming language \emph{Stan} (\emph{11}). We used CmdStan version
2.33.1 and \textbf{cmdstanr} version 0.7.1 (\emph{12}) to interface with
\emph{R} version 4.3.2 (\emph{13}). We sampled the posterior
distribution from 4 chains with 1000 iterations each after 1000 warmup
iterations per chain. We estimated parameters and confidence intervals
as the median and 95\% quantile intervals of the posterior,
respectively.

\paragraph{Parameter estimation}\label{parameter-estimation}

There were four levels of parameter estimation in our analysis:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Estimate \agcurve{} curve parameters for each leaf
\item
  Estimate \aax{} for each light intensity with leaf using \agcurve{}
  curve parameters
\item
  Estimate the effects of light intensity, light treatment, and
  accession on \aax{} (assimilatory and plasticity hypotheses)
\item
  Estimate the effects of native light habitat on accession-level \aax{}
  (constitutive hypothesis)
\end{enumerate}

Although the higher-level parameter estimates depend on the lower-level
parameter estimates, we fit all models simultaneously to ensure that the
uncertainty in lower-level estimates propagated to higher-level
estimates.

\subparagraph{\texorpdfstring{\agcurve{} curve
parameters}{ curve parameters}}\label{curve-parameters}

We modeled \logA as a quadratic function of \loggsw for each leaf using
the following equation:

\[\log(A_{ij}) = (\beta_0 + b_{0,j}) + (\beta_1 + b_{1,j}) \log{g_{\text{sw},i}} + (\beta_2 + b_{2,j}) \log{g_{\text{sw},i}}^2 + \epsilon_{i}\]

where \(\beta_0\), \(\beta_1\), and \(\beta_2\) are the average
intercept, linear, and quadratic coefficients, respectively. We used
diffuse normal priors with mean \(0\) and standard deviation \(10\) on
these parameters. We estimated random effects of curve \(j\) on the
intercept (\(b_{0,j}\)), linear (\(b_{1,j}\)), and quadratic
(\(b_{2,j}\)) coefficients. We assumed that the \(j \times 3\) array of
coefficients was multivariate normal a mean vector of \(\vec{0}\) and
covariance \(\Sigma_\text{curve}\). We used a weakly informative normal
prior with mean \(0\) and standard deviation \(1\) on the
log-transformed standard deviations (i.e.~the diagonal of
\(\Sigma_\text{curve}\)). We used a weakly informative
\(\mathrm{LJK}(2)\) prior on the correlation matrix. The off diagonal
elements of \(\Sigma_\text{curve}\) can be calculated from its diagonal
elements and the correlation matrix.

The residuals \(\epsilon_{i}\) were modeled as a lag-1 autocorrelated
time-series. We further assumed that the residual standard deviation of
the \(j^{\text{th}}\) curve (\(\sigma_{\epsilon,j}\)) was inversely
proportional to the leaf surface area (\(S_j\)) within the chamber:

\[\log (\sigma_{\epsilon,j}) = \log (\sigma_{\qty{6}{\raiseto{2}\centi\meter},\epsilon}) + (6 - S_j) \beta_{S,\epsilon}\]
where \(\sigma_{\qty{6}{\raiseto{2}\centi\meter},\epsilon}\) is the
minimum residual standard deviation when the
\(\qty{6}{\raiseto{2}\centi\meter}\) chamber is completely filled. The
residual standard deviation increases on log-linear scale by
\(\beta_{S,\epsilon}\). We used a weakly informative normal prior with
mean \(-3\) and standard deviation \(5\) on
\(\log (\sigma_{\qty{6}{\raiseto{2}\centi\meter},\epsilon})\) and a
weakly informative normal prior with mean \(0\) and standard deviation
\(1\) on \(\beta_{S,\epsilon}\).

\subparagraph{\texorpdfstring{\aax{} for each light intensity with leaf
using \agcurve{} curve
parameters}{ for each light intensity with leaf using  curve parameters}}\label{for-each-light-intensity-with-leaf-using-curve-parameters}

Within the \(k^{\text{th}}\) leaf, we estimated \aax{} for each light
intensity by integrating the difference in \logA between the amphi and
pseudohypo \agcurve{} curves over the range of \gsw{} values where the
curves overlap. We used the following equation to estimate \aax{} for
the \(k^{\text{th}}\) leaf at light intensity \(l\) in accession \(m\):

\[\widehat{\mathrm{AA}}_{klm} = \int_{\text{min(log(}g_\text{sw}))}^{\text{max(log(}g_\text{sw}))} \text{log}\bigg(\frac{\hat{A}_\text{amphi}(x; \theta_{klm,\text{amphi})}}{\hat{A}_\text{hypo}(x; \theta_{klm,\text{hypo})}}\bigg) dx\]
where:

\[\theta_\text{amphi} \in \{\hat{b}_{0, f(\text{amphi}, k,l,m)}, \hat{b}_{1, f(\text{amphi}, k,l,m)}, \hat{b}_{2, f(\text{amphi}, k,l,m)}\}, \text{and}\]

\[\theta_\text{hypo} \in \{\hat{b}_{0, f(\text{hypo}, k,l,m)}, \hat{b}_{1, f(\text{hypo}, k,l,m)}, \hat{b}_{2, f(\text{hypo}, k,l,m)}\}.\]
The function \(f : \Theta_1 \rightarrow \Theta_2\) maps the set
\(\Theta_1\) indexed by leaf type (amphi or pseudohypo), leaf replicate,
light intensity, and accession to set \(\Theta_2\) indexed by \agcurve{}
curve.

WORKING HERE

We estimated these parameters for each leaf using the posterior
distribution of the parameters from the \agcurve{} curve fitting
procedure.

@@

@@

We tested competing predictions through a combination of model selection
and parameter estimation from the posterior of selected models. We
started with a base model that includes fixed effects of light intensity
and light treatment on \aax, a random effect of accession on \aax, and a
linear regression of PAR on accession-level \aax. We next compared the
fit of the base model to a more complex with an interaction between
light intensity and light treatment using LOOIC with the \textit{R}
package \textbf{loo} version 2.7.0 (\emph{14}). These comparisons
allowed us to test the main predictions of each hypothesis and for a
reinforcing interactions between assimilatory and plastic hypotheses
(tab:predictions). However, these models cannot test predictions when
there is an interaction with the constitutive hypothesis, because this
hypothesis posits accession-levels variation in responses to light
intensity and/or light treatment. Therefore, we tested for significant
variation among accessions in light intensity and light treatment by
comparing LOOIC values of models with and without random interactions
between these factors and accession.

@@

\bibitem[\citeproctext]{ref-marshall_model_1980}
\CSLLeftMargin{8. }%
\CSLRightInline{B. Marshall, P. V. Biscoe,
\href{https://doi.org/10.1093/jxb/31.1.29}{A {Model} for
{C}\(_{\textrm{3}}\) {Leaves} {Describing} the {Dependence} of {Net}
{Photosynthesis} on {Irradiance}}. \emph{Journal of Experimental Botany}
\textbf{31}, 29--39 (1980).}

\bibitem[\citeproctext]{ref-elzhov_minpacklm_2023}
\CSLLeftMargin{9. }%
\CSLRightInline{T. V. Elzhov, K. M. Mullen, A.-N. Spiess, B. M. Bolker,
\emph{Minpack.lm: {R} {Interface} to the {Levenberg}-{Marquardt}
{Nonlinear} {Least}-{Squares} {Algorithm} {Found} in {MINPACK}, {Plus}
{Support} for {Bounds}} (2023;
\url{https://CRAN.R-project.org/package=minpack.lm}).}

\bibitem[\citeproctext]{ref-gelman_inference_1992}
\CSLLeftMargin{10. }%
\CSLRightInline{A. Gelman, D. B. Rubin, Inference from iterative
simulation using multiple sequences. \emph{Statistical Science}
\textbf{7}, 457--472 (1992).}

\bibitem[\citeproctext]{ref-stan_development_team_stan_2023}
\CSLLeftMargin{11. }%
\CSLRightInline{Stan Development Team, \emph{Stan {Modeling} {Language}
{Users} {Guide} and {Reference} {Manual}} (2023;
\url{https://mc-stan.org}).}

\bibitem[\citeproctext]{ref-gabry_cmdstanr_2023}
\CSLLeftMargin{12. }%
\CSLRightInline{J. Gabry, R. Češnovar, \emph{Cmdstanr: {R} {Interface}
to '{CmdStan}'} (2023;
\href{https://mc-stan.org/cmdstanr,\%20https://discourse.mc-stan.org}{https://mc-stan.org/cmdstanr,
https://discourse.mc-stan.org}).}

\bibitem[\citeproctext]{ref-r_core_team_r:_2023}
\CSLLeftMargin{13. }%
\CSLRightInline{R Core Team, \emph{R: {A} {Language} and {Environment}
for {Statistical} {Computing}} (R Foundation for Statistical Computing,
Vienna, Austria, 2023; \url{http://www.R-project.org/}).}

\bibitem[\citeproctext]{ref-vehtari_practical_2017}
\CSLLeftMargin{14. }%
\CSLRightInline{A. Vehtari, A. Gelman, J. Gabry,
\href{https://doi.org/10.1007/s11222-016-9696-4}{Practical {Bayesian}
model evaluation using leave-one-out cross-validation and {WAIC}}.
\emph{Statistics and Computing} \textbf{27}, 1413--1432 (2017).}
